---
output: rmarkdown::github_document
---

`bgpdump` : Tools to Retrieve and Process 'BGP' Files

### Requirements

This package links to [`libBGPdump`](https://bitbucket.org/ripencc/bgpdump/wiki/Home).

On macOS, you can:

    brew install bgpdump
    

On Ubuntu/Debian (or prbly any other one) you can:

    sudo apt-get install -y mercurial libbz2-dev zlib1g-dev
    hg clone https://bitbucket.org/ripencc/bgpdump
    cd bgpdump
    ./bootstrap.sh
    make
    sudo make install
    

The following functions are implemented:

- `get_latest_rib`:	Retrieve the latest RouteViews RIB file
- `get_rib`:	Retrieve a specific, historical RouteViews RIB file
- `rib_to_asn_table`:	Convert RouteViews RIB (bgpdump table dump v2) to subnet/asn map

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/bgpdump")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(bgpdump)

# current verison
packageVersion("bgpdump")

```

### Test Results

```{r}
library(bgpdump)
library(testthat)

date()

test_dir("tests/")
```

